---
title: "imf-api"
author: "JF"
date: "1/11/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This script explores a new package, 'imfr', which exists to download data from the International Monetary Fund's Data API

NOTE: As of 10 January, 2017, I haven't been able to get this package to work. I get an error whenever running anything.

Anyway, here's some code on the package, unevaluated for now.

```{r imfr_test, eval=FALSE}
# install.packages("imfr")
library(imfr)

real_ex <- imf_data(database_id = 'IFS', indicator = 'EREER_IX',
                    country = c('CN', 'GB'), freq = 'A',
                    start = 2013, end = current_year())

all_iso2c() # Data frame of 253 ISO two letter country codes 

imf_codelist("4", return_raw = TRUE, times = 3) # Retrieve the code list of codes 
# (codelist) for an individual IMF database.

imf_codes(codelist, return_raw = FALSE, times = 3) # Retrieve individual database codes

imf_data() # Download data from the IMF

imf_ids(return_raw = TRUE, times = 3) # Lists the IMF database IDs

# Note that the IFS id is '4' and that there are about 75 different databases 
# included here.
```

### IMF API Application

Here I use IMF data to calculate the CIM measure discussed in Clague et al. (1999).

Calculating CIM requires two variables, M2 (money supply) and C (currency held outside of banks). CIM is given as $(M2-C)/M2$.

M2: Money and quasi money (M2) comprise the sum of currency outside banks, 
demand deposits other than those of the central government, and the time, 
savings, and foreign currency deposits of resident sectors other than the 
central government. This definition of money supply is frequently called M2; it corresponds to lines 34 and 35 in the International Monetary Fund's 
International Financial Statistics. Data are in current local currency.

C: Currency held outside of banks, given in local currency.

Note: Currency units are given in national currency

Here's (unevaluated) code calculating the index.

```{r cim, eval=FALSE}

### Downloads the M2 variable for the countries of the world at an annual frequency

library(imfr)
imf_codelist(database_id = "4", return_raw = TRUE, times = 3)

# Returns the codelist for indicators in the IMF IFS. Note that 'return_raw = FALSE' returns a data frame with codelist codes and descriptions.

m2 <- imf_data(database_id = "4", indicator = "?", country = "all", start = 1960,
  end = current_year(), freq = "A", return_raw = FALSE,
  print_url = TRUE, times = 3)

c <- imf_data(database_id = "4", indicator = "?", country = "all", start = 1960,
  end = current_year(), freq = "A", return_raw = FALSE, print_url = TRUE, 
  times = 3)

cim <- (m2-c)/m2

```